Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-12 firstPaper/corrections/replyToReferee.txt

We thank the referee for their helpful comments.  We have tried to implement them
all.  Below are our replies to each comment.  We have also made a few additional
changes, which we first list.

(a) In Notation 1.50, the equalities were wrong and have been corrected.

(b) We have added some details (in a new Proposition 2.24) explaining why the non-kissing facets are finite. In doing so, we had to slightly reorganise Subsection 2.2.2 (new Lemma 2.23 was previously part of the proof of Proposition (renumbered) 2.28)

### 2018-07-12 draft/accordionComplexSurfaces.tex
relecture section 6 fin

\begin{definition}
\label{def:kissingNumber}
For two walks~$\omega$ and~$\omega'$ of~$\bar Q$, denote by~$\kn(\omega,\omega')$ the number of kisses of~$\omega$ to~$\omega'$.
Note that kisses are counted with multiplicities if~$\omega$ or~$\omega'$ pass twice through the same substring.
Observe also that~$\kn(\omega,\omega')$ is finite since any infinite walk is eventually cyclic.
The \defn{kissing number} of~$\omega$ and~$\omega'$ is~$\KN(\omega,\omega') \eqdef \kn(\omega,\omega') + \kn(\omega',\omega)$.
%Since~$\RNKC$ is finite, we can define the \defn{kissing number} of a walk~$\omega$ on~$\bar Q$ as
%\[
%\KN(\omega) \eqdef \sum_{\omega'} \KN(\omega,\omega'),
%\]
%where the sum runs over all walks~$\omega'$ of~$\NKWalks^\pm(\bar Q)$.
\end{definition}

@@

\begin{example}
\label{exm:gcdVectorsWalks}
For instance, the $\b{g}$-, $\b{c}$-, and $\b{d}$-matrices of the facet illustrated in \fref{fig:gcdVectors} are given by
\[
\gvectors{F} = 
\begin{blockarray}{ccc}
	{\color{blue} \bullet} & {\color{purple} \bullet} & \\[-.1cm]
	\begin{block}{[cc]c}
	1 & 0 & \!\!\!\circled{1} \\
	-1\!\! & \!\!-1 & \!\!\!\circled{2} \\
	\end{block}
\end{blockarray}
\qquad\qquad
\cvectors{F} = 
\begin{blockarray}{ccc}
	{\color{blue} \bullet} & {\color{purple} \bullet} & \\[-.1cm]
	\begin{block}{[cc]c}
	1 & \!\!-1 & \!\!\!\circled{1} \\
	0 & \!\!-1 & \!\!\!\circled{2} \\
	\end{block}
\end{blockarray}
\qquad\qquad
\dvectors{F} = 
\begin{blockarray}{ccc}
	{\color{blue} \bullet} & {\color{purple} \bullet} & \\[-.1cm]
	\begin{block}{[cc]c}
	1 & 0 & \!\!\!\circled{1} \\
	0 & -1 & \!\!\!\circled{2} \\
	\end{block}
\end{blockarray}
\]
(\ie columns are the $\b{g}$-, $\b{c}$-, $\b{d}$-vectors of the elements of the facet).

@@

\begin{proposition}
\label{prop:gVectorsSurface}
For a walk~$\omega$ of~$\bar Q$ and a vertex~$p \in Q_0$, the $p$th entry of the $\b{g}$-vector~$\gvector{\omega}$ is given~by
\begin{enumerate}[(i)]
\item The number of times that the $\dissection$-accordion~$\curveof(\omega)$ positively crosses the edge~$\edgeof(p)$ of~$\dissection$ minus the number of times it negatively crosses the edge~$\edgeof(p)$ of~$\dissection$. Here, the crossing is positive (resp.~negative) if the two angles of~$\dissection$ crossed by~$\curveof(\alpha)$ just before and after~$\edgeof(p)$ form a~$\SSS$ (resp.~as a~$\ZZZ$).
\item The number of times that the $\dissection\dual$-slalom~$\curveof(\omega)$ positively crosses the edge~$\dualedgeof(p)$ of~$\dissection\dual$ minus the number of times it negatively crosses the edge~$\dualedgeof(p)$ of~$\dissection\dual$. Here, the crossing is positive when~$\curveof(\omega)$ leaves a face~$u\dual$ to enter a face~$v\dual$ with the vertex~$u$ being to its right (and thus with~$v$ being to its left), and the crossing is negative otherwise.
\end{enumerate}
\end{proposition}

\begin{proposition}
\label{prop:cVectorsSurface}
Consider a walk~$\omega$ of~$\bar Q$ in a non-kissing facet~$F \in \RNKC$.
Call \defn{distinguished subcurve} of~$\curveof(\omega)$ in~$\curveof(F)$ the part of~$\curveof(\omega)$ which lies strictly between the two angles of~$\dissection$ (or of~$\dissection\dual$) where~$\curveof(\omega)$ is maximal (see Remark~\ref{rem:countercurrentOrderOnSurface}).
For a vertex~$p \in Q_0$, the $p$th entry of the $\b{c}$-vector~$\cvector{\omega}{F}$ is given by
\begin{enumerate}[(i)]
\item the number of crossings between the distinguished subcurve of~$\curveof(\omega)$ in~$\curveof(F)$ and the edge~$\edgeof(v)$ of the dissection~$\dissection$,
\item the number of times the distinguished subcurve of~$\curveof(\omega)$ in~$\curveof(F)$ follows the edge~$\dualedgeof(v)$ of the dual dissection~$\dissection\dual$. Here, we say that a curve~$\delta$ follows~$\dualedgeof(v)$ if~$\dualedgeof(v)$ lies on the boundary opposite to~$u$ of a face~$u\dual$ of~$\dissection\dual$ crossed by~$\delta$.
\end{enumerate}
\end{proposition}

@@

\begin{proposition}
\label{prop:dVectorsSurface}
Denote by~$X_\deep$ the deep facet of the non-crossing complex as described in Example~\ref{exm:peakDeepFacets}.
For a walk~$\omega$ of~$\bar Q$ and a vertex~$p \in Q_0$, the $p$th entry of the $\b{d}$-vector~$\dvector{\omega}$ is the number of crossings of the curve~$\gamma(\omega)$ with the edge of~$X_\deep$ corresponding to~$p$.
\end{proposition}

@@

\begin{proof}
For the $\b{g}$-vectors, observe that two walks~$\omega$ and~$\omega'$ whose $\b{g}$-vectors~$\gvector{\omega}$ and~$\gvector{\omega}$ have opposite signs on their~$v$th coordinate automatically kiss at~$v$.
For $\b{c}$- and $\b{d}$-vectors, the statement is immediate from the definition.
\end{proof}

>>>>

\begin{definition}
\label{def:kissingNumber}
For two walks~$\omega$ and~$\omega'$ of~$\bar Q$, denote by~$\kn(\omega,\omega')$ the number of times that~$\omega$ kisses $\omega'$.
Note that kisses are counted with multiplicities if~$\omega$ or~$\omega'$ pass twice through the same substring.
Observe also that~$\kn(\omega,\omega')$ is finite since any infinite walk is eventually cyclic.
The \defn{kissing number} of~$\omega$ and~$\omega'$ is~$\KN(\omega,\omega') \eqdef \kn(\omega,\omega') + \kn(\omega',\omega)$.
%Since~$\RNKC$ is finite, we can define the \defn{kissing number} of a walk~$\omega$ on~$\bar Q$ as
%\[
%\KN(\omega) \eqdef \sum_{\omega'} \KN(\omega,\omega'),
%\]
%where the sum runs over all walks~$\omega'$ of~$\NKWalks^\pm(\bar Q)$.
\end{definition}

@@

\begin{example}
\label{exm:gcdVectorsWalks}
For instance, the $\b{g}$-, $\b{c}$-, and $\b{d}$-matrices of the facet illustrated in \fref{fig:gcdVectors} are given by
\[
\gvectors{F} = 
\begin{blockarray}{ccc}
	{\color{blue} \bullet} & {\color{violet} \bullet} & \\[-.1cm]
	\begin{block}{[cc]c}
	1 & 0 & \!\!\!\circled{1} \\
	-1\!\! & \!\!-1 & \!\!\!\circled{2} \\
	\end{block}
\end{blockarray}
\qquad\qquad
\cvectors{F} = 
\begin{blockarray}{ccc}
	{\color{blue} \bullet} & {\color{violet} \bullet} & \\[-.1cm]
	\begin{block}{[cc]c}
	1 & \!\!-1 & \!\!\!\circled{1} \\
	0 & \!\!-1 & \!\!\!\circled{2} \\
	\end{block}
\end{blockarray}
\qquad\qquad
\dvectors{F} = 
\begin{blockarray}{ccc}
	{\color{blue} \bullet} & {\color{violet} \bullet} & \\[-.1cm]
	\begin{block}{[cc]c}
	1 & 0 & \!\!\!\circled{1} \\
	0 & -1 & \!\!\!\circled{2} \\
	\end{block}
\end{blockarray}
\]
(\ie columns are the $\b{g}$-, $\b{c}$-, $\b{d}$-vectors of the elements of the facet).

@@

\begin{proposition}
\label{prop:gVectorsSurface}
For a walk~$\omega$ of~$\bar Q$ and a vertex~$p \in Q_0$, the $p$-th entry of the $\b{g}$-vector~$\gvector{\omega}$ is given~by:
\begin{enumerate}[(i)]
\item The number of times that the $\dissection$-accordion~$\curveof(\omega)$ positively crosses the edge~$\edgeof(p)$ of~$\dissection$ minus the number of times it negatively crosses the edge~$\edgeof(p)$ of~$\dissection$. Here, the crossing is positive (resp.~negative) if the two angles of~$\dissection$ crossed by~$\curveof(\alpha)$ just before and after~$\edgeof(p)$ form a~$\SSS$ (resp.~as a~$\ZZZ$).
We note that some crossings are neither positive nor negative.
\item The number of times that the $\dissection\dual$-slalom~$\curveof(\omega)$ positively crosses the edge~$\dualedgeof(p)$ of~$\dissection\dual$ minus the number of times it negatively crosses the edge~$\dualedgeof(p)$ of~$\dissection\dual$. Here, the crossing is positive when~$\curveof(\omega)$ leaves a face~$u\dual$ to enter a face~$v\dual$ with the vertex~$u$ being to its right (and thus with~$v$ being to its left), and the crossing is negative otherwise.
We note that, in this case, each crossing is either positive or negative.
\end{enumerate}
\end{proposition}

\begin{proposition}
\label{prop:cVectorsSurface}
Consider a walk~$\omega$ of~$\bar Q$ in a non-kissing facet~$F \in \RNKC$.
Call \defn{distinguished subcurve} of~$\curveof(\omega)$ in~$\curveof(F)$ the part of~$\curveof(\omega)$ which lies strictly between the two angles of~$\dissection$ (or of~$\dissection\dual$) where~$\curveof(\omega)$ is maximal (see Remark~\ref{rem:countercurrentOrderOnSurface}).
For a vertex~$v \in Q_0$, the $v$-th entry of the $\b{c}$-vector~$\cvector{\omega}{F}$ is given by
\begin{enumerate}[(i)]
\item the number of crossings between the distinguished subcurve of~$\curveof(\omega)$ in~$\curveof(F)$ and the edge~$\edgeof(v)$ of the dissection~$\dissection$,
\item the number of times the distinguished subcurve of~$\curveof(\omega)$ in~$\curveof(F)$ follows the edge~$\dualedgeof(v)$ of the dual dissection~$\dissection\dual$. Here, we say that a curve~$\delta$ follows~$\dualedgeof(v)$ if~$\dualedgeof(v)$ lies on the boundary opposite to~$u$ of a face~$u\dual$ of~$\dissection\dual$ crossed by~$\delta$.
\end{enumerate}
\end{proposition}

@@

\begin{proposition}
\label{prop:dVectorsSurface}
Denote by~$X_\deep$ the deep facet of the non-crossing complex as described in Example~\ref{exm:peakDeepFacets}.
For a walk~$\omega$ of~$\bar Q$ and a vertex~$v \in Q_0$, the $v$-th entry of the $\b{d}$-vector~$\dvector{\omega}$ is the number of crossings of the curve~$\gamma(\omega)$ with the edge of~$X_\deep$ corresponding to~$v$.
\end{proposition}

@@

\begin{proof}
For the $\b{g}$-vectors, observe that two walks~$\omega$ and~$\omega'$ whose $\b{g}$-vectors~$\gvector{\omega}$ and~$\gvector{\omega}$ have opposite signs on their~$v$-th coordinate automatically kiss at~$v$.
For $\b{c}$- and $\b{d}$-vectors, the statement is immediate from the definition.
\end{proof}
